---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo=TRUE,
  comment = "#>"
)
```

# walkability_zillowMap

<!-- badges: start -->
<!-- badges: end -->

An application that visualizes the walkability and Zillow listings within an isochrone. Currently designed for the Denver metro.

Run the app with the following. See below for more set up details.

```{r,eval=FALSE}
shiny::runGitHub("jzemmels/walkability_zillowMap",subdir = "zillow-walkability")
```

We assume that you have some R and Python libraries installed on your machine.
The code below will install the required packages.

```{r,eval=FALSE}
# required R packages
install.packages(c("tidyverse","shiny","shinyWidgets","reticulate","leaflet"))

# required Python libraries
reticulate::py_install(c("httpx","pandas"),pip=TRUE)
```

Note that you may need to set up Python using the `reticulate` R package.
See <https://rstudio.github.io/reticulate/> for more information.
The Python dependency is isolated to the Zillow housing data scraping, so you can just not use that functionality if you don't want to worry about Python.
